---
title: "Markdown_Project2"
author: "Christiana"
date: "5/3/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

# *Does Automation improve firm performance, and investment and labor efficiency?*
 
## Background 
There is increasing interest in automation and other workforce technologies that disrupt conventional business practices and the competitive landscape. This is especially true in the manufacturing sector, an industry in which a shift from manual processes to automation is most prevalent. This includes automated assembly lines using robots equipped with sensors, autonomous vehicles, predictive analytics applications with embedded artificial intelligence algorithms, and blockchain for enterprise resource planning and/ or supply chain management. Economists see the manufacturing sector as an industry that has the highest potential to benefit from increased automation as it can provide higher levels of output, better quality, and fewer errors; however, despite the obvious potential benefits, about three percent of all goods produced are the result of automated processes. Against this background, this report addresses two important issues.  First, I provide descriptive evidence on the adoption of automation in manufacturing firms that are members of the S&P 1500 index over the last three decades.  Second, I examine the impact of automation on labor efficiency. 

## Motivation 
Note that the need for automation in manufacturing has become even more apparent as firms have been affected by the global COVID-19 pandemic, exposing vulnerabilities in global supply chains and production scale and leaving millions of workers in various sectors (including manufacturing) unemployed at a rapid pace. According to a March 2020 survey from the National Association of Manufacturers, about 53 percent of manufacturing firms expect a change in operations due to the pandemic. As such, firms in the manufacturing sector are under renewed pressure to evolve their production processes while maintaining low costs and reasonable quality. Contracting and sourcing for automation equipment has increased by 150% from 2019 to 2020 and it is expected that automation will become faster and easier to deploy in the near future.

## Research Design and Data 
I begin the sample selection process by identifying the manufacturing firms that are members of the Standard and Poor’s (S&P) 1500 index as of 2019, based on the Standard Industrial Classification (SIC) industry codes 2000-3990 in Compustat. There are approximately 578 manufacturing firms in the S&P 1500 index as of 2019. The sample period starts from the year 1994 and runs through 2019. In addition, I use the annual 10-K filings that disclose the addition or investment in automation in manufacturing processes and/or operations based on word/phrase searches.

```{r data, echo=FALSE, include=FALSE}
#Bring in Data
s1data<-read.csv("https://github.com/Christiana1826/Project2/SummerIdata.csv")

myvars<-c("automation_disclosure", "count_keywords_usage", "year", "at", "lifecycle", "firstterm", "lnat", "at", "mtb", "firmage", "lnfirmage", "loss", "dividend", "debt", "roa", "ffind", "fasset_turn", "fineffnethire", "restructuring_dum", "workforce_reduc_dum")
s1data2<-s1data[myvars]
names(s1data2)

summary(s1data2)
```

Based on the summary statistics above, about 6 percent of the firms in the sample had an automation disclosure within their 10-K annual report (automation_disclosure). The maximum number of times that automation is mentioned by a firm in an annual report is 8 (count_keyword_usage). The mean total assets (at) of the firms is $8.06 million, and the mean firm age (firmage) is 26 years. The mean life cycle ratio is 1.74, which suggests that most firms are between growth and mature stages (lifecycle). About 16.4 percent of the firms reported negative net income (variable: loss) and almost all (99.6 percent) firms paid dividends (variable: dividend). The mean unconditional likelihood of a firm engaging in a restructuring event and employee layoff is 41 percent and 25 percent, respectively (restructuring_dum, workforce_reduc_dum).

## Findings: Keyword Distribution
The visual shown below includes the specific keywords used in annual 10-K reports over the sample period. The keyword “automation” is used most frequently (67%) which is reasonable given this is a more general term for describing the adoption of technology into manufacturing processes.  

```{r visuals_1, echo=FALSE, include=TRUE, warning=FALSE}
keywords<-table(s1data2$firstterm[s1data2$automation_disclosure==1])
barplot(keywords, main="Keyword Distribution", xlab="keyword")

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.



## Findings: Industry Distribution
The visual shown below is the sample distribution based on the Fama-French industries. The largest representation in the sample are industries 36 (Electronic Equipment), 13 (Pharmaceutical Products), 21 (Machinery), 12 (Medical Equipment), and 14 (Chemicals). This makes sense because these Fama-French industries consist of the Standard Industrial Classification (SIC) industry codes for manufacturing (SIC 2000-3990). Likewise, the sample distribution by industry excludes non-manufacturing industries, such as business services, construction, telecommunications, retail, and transportation. 

```{r visuals_2, echo=FALSE, include=TRUE, warning=FALSE}
industry<-table(s1data2$ffind[s1data2$automation_disclosure==1])
barplot(industry, main="Industry Distribution", xlab="Fama-French industries")

```


## Findings: Automation Disclosure by Year
The visual shown below presents the sample distribution of automation keywords by year. This table shows the firm-year observations conditional on having an automation disclosure in the annual 10-K report. Over time, there has been an increase in the firms disclosing automation, suggesting the firms that adopt automation has been increasing over time. Most importantly, this provides preliminary evidence that manufacturing firms are increasingly adopting over the time period 1994-2019. 

```{r visuals_3, echo=FALSE, include=TRUE, warning=FALSE}
by_year<-table(s1data2$year[s1data2$automation_disclosure==1])
barplot(by_year, main="Automation Disclosure by Year", xlab="Year")


```